### 2021-11-16 article/article.tex
Merged changes from Josh and Joel

\section{Paper Author Roles and Affiliations}
1. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Primary author of the released packages.\\
2. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Present address: Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
	Author of first version of code.\\
3. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Present address: School of Physics, University of Sydney, NSW 2006, Australia.\\
	Optimization and extension to spin-one of first version of code.\\
4. School of Molecular Sciences, La Trobe University, PO box 199, Bendigo, Victoria 3552, Australia.\\
	Present address: Q-CTRL Pty. Ltd.\\
	Original conception of first version, and advice on current version of code.\\
5. Department of Electrical and Computer Systems Engineering, Monash University, Victoria 3800, Australia.\\
	Advice on numerical analysis.\\
6. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Original conception of released version of algorithm.

\section{Abstract}
	The \emph{Spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shroedinger equation.
	It makes use of \texttt{numba.cuda}, which is an \emph{LLVM} (Low Level Virtual Machine) compiler for \emph{Nvidia Cuda} compatible systems using GPU parallelization. 
	Along with other optimizations, this allows for speed improvements of up to four orders of magnitude while staying just as accurate, compared to industry standard packages.
	It is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
	The initial use-case for the \emph{Spinsim} will be to simulate quantum sensing-based ultracold atom experiments for the Monash University School of Physics \& Astronomy spinor Bose-Einstein condensate (spinor BEC) lab, but we anticipate it will be useful in simulating any range of spin-half or spin-one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
	These appear in the fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin-one systems of nitrogen vacancy centres (NVCs), ultracold atoms, and BECs.

@@

\section{Introduction}
\subsection{Motivation}
	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing~\cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
	The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
	The simplest spin system, spin-half (ie spin quantum number of $ \frac12 $, also referred to as a qubit), is quantized into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (ie spin quantum number of $ 1 $, also referred to as a quitrit), which is quantized into three quantum spin levels.

@@

	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours, or even multiple days.
	Given the recent boom in machine learning, many research computers are now equipped with modern graphics processing units (GPUs).
	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
	Examples include calculating color values for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
	While there do exists parallelized algorithms to solve general differential equations~\cite{lions_resolution_2001}, there are properties specific to the spin system that allow for much more fast and elegant parallelization in our use-case.
	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by three orders of magnitude.
	% Mention GPU in fewer words

@@

\section{Implementation and architecture}
	% \subsection{Mathematical methods}
	\subsection{Quantum mechanics background}
		The \emph{Spinsim} package solves the time-dependent Schr\"{o}dinger equation
		\begin{align}
			i\hbar\frac{\mathrm{d}\psi(t)}{\mathrm{d}t} &= H(t)\psi(t),\label{eq:schroedinger}
		\end{align}
		where the quantum state $ \psi(t) \in \mathbb{C}^N $ is assumed normalized, and the Hamiltonian $ H(t) \in \mathbb{C}^{N \times N} $ is Hermitian.
		Here $ N $ is the number of levels in the quantum system.
		Often we are considering systems with spin of half or one.
		Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
		% \supervisordisagreement{
		% 	Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
		% }{
		% Spin-half is the $ N = 2 $ case, and spin-one is the $ N = 3 $ case.
		% }
		We set $ \hbar = 1 $, so that the Hamiltonian has physical dimension of angular frequency.
		% Furthermore, we have chosen for the Hamiltonian $ H(t) $ to have the physical dimension of frequency, rather than the more typical dimension of energy. To elaborate, we represent energies $ E $ of the system as their equivalent frequencies $ f $ from the Planck relation

@@

		Rather than parametrizing the problem in terms of the matrix elements of $ H(t) $, we consider time varying real coefficients in a linear combination of fixed operators,
		\begin{align}
			H(t) &= \sum_{j = 1}^{N^2 - 1} \omega_j(t) \mathcal{A}_j.
		\end{align}
		Here we exclude the identity so that the Hamiltonian is traceless, which corresponds to choosing a physically meaningless energy zero point.
		It is well known that a charged spin-half system with magnetic moment $ \overrightarrow{\mu} $, and gyromagnetic ratio $ \gamma $, in a magnetic field $ \overrightarrow{B}(t) $, has Hamiltonian
		\begin{align}
			H(t) &= -\overrightarrow{B}(t)\cdot \overrightarrow{\mu}\\
			% &= -\gamma \overrightarrow{B}(t)\cdot \overrightarrow{J}\\
			&= -\gamma \left(B_x(t) J_x + B_y(t) J_y + B_z(t) J_z\right)\\
			% &= \left(-\gamma B_x(t) J_x\right) + \left(-\gamma B_y(t) J_y\right) + \left(-\gamma B_z(t) J_z\right)\\
			&= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z.
		\end{align}
		Here $ J_x $, $ J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices~\cite[(p169)]{j_j_sakurai_jun_john_modern_2011} halved.
		% \supervisordisagreement{
		% 	Here $ J_x, J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices halved.
		% }{
		% 	Here $ J_x, J_y $ and $ J_z $ are spin operators
		% 	\begin{align}
		% 		J_x &= \frac12\begin{pmatrix}
		% 			0 & 1 \\
		% 			1 & 0
		% 		\end{pmatrix},
		% 		&J_y &= \frac12\begin{pmatrix}
		% 			0 & -i \\
		% 			i &  0
		% 		\end{pmatrix},
		% 		&\textrm{and }J_z &= \frac12\begin{pmatrix}
		% 			1 &  0 \\
		% 			0 & -1
		% 		\end{pmatrix},\label{eq:spin_half_operators}
		% 	\end{align}
		% 	equal to the Pauli matrices halved.
		% }
		Because of the equivalence of the magnetic field components $ B_j(t) $ and the $ \omega_j(t) $, we henceforth refer to the latter as field functions.

		In the spin-one case there is no standard basis of operators $ \mathcal{A}_j $.
		Choices include the Gell-Mann matrices~\cite{gell-mann_symmetries_1962}, and multiple dipole-quadrupole bases~\cite{hamley_spin-nematic_2012, di_dipolequadrupole_2010}.
		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
		We focus on a particular subfamily of of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x $, $ J_y $ and $ J_z $, (labelled $ L_x $, $ L_y $ and $ L_z $ in Reference~\cite{hamley_spin-nematic_2012}) and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,% \todo{Describe this subspace better}

@@

		% With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,
		\begin{align}
			H(t) &= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q.
		\end{align}

		Note that $ Q $ is proportional to $ J_z^2 $ (up to a change in energy zero point), and $ Q_{zz} $~\cite{hamley_spin-nematic_2012} and $ Q_0 $~\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
		The $ J_x $, $ J_y $, $ J_z $ and $ Q $ are the only operators necessary to simulate many spin-one quantum systems in arbitrary bias fields, but with single-photon coupling.
		This includes quadratic Zeeman splitting described by the Breit-Rabi formula~\cite{mockler_atomic_1961} important to experiments in our lab.
		The \emph{Spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $ using the full quadrupole basis, which extends the possible Hamiltonian to
		\begin{align}
			H(t) =& \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q\nonumber\\
			&+ \omega_{u1}(t) U_1 + \omega_{u2}(t) U_2 + \omega_{v1}(t) V_1 + \omega_{v2}(t) V_2.
		\end{align}
		Here the additional operators are those defined in~\cite{di_dipolequadrupole_2010}. Note that this is included for completeness, but has not been thoroughly tested, as our lab has no physical context for modelling the $ U_1, U_2, V_1 $ and $ V_2 $ operators.
		% In general ... Lie algebra ... mathfrak ... admits a basis ... .
		% \begin{align}
		% 	\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z) \psi(t),
		% \end{align}

@@

		% \begin{align}
		% 	\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z + f_q(t) Q) \psi(t).
		% \end{align}

@@

	\subsection{Unitary time evolution and the Magnus expansion}\label{sec:magnus}
		Since $H(t)$ is Hermitian, it follows from Equation~\eqref{eq:schroedinger} that $\|\psi(t)\|^2 = \|\psi(t_0)\|^2$ for all $t$.
		Therefore it is possible to write $ \psi(t) $ in terms of a unitary transformation $ \mathcal{U}(t, t_0) $ of the state $ \psi(t_0) $, for any time $ t_0 $, that is, $ \psi(t) = \mathcal{U}(t, t_0)\psi(t_0) $.
		It then follows from Equation~\eqref{eq:schroedinger} that $ \mathcal{U}(t, t_0) $ also follows a Schr\"{o}dinger equation,
		\begin{align}
			i\hbar\frac{\mathrm{d}\mathcal{U}(t, t_0)}{\mathrm{d}t} &= H(t)\mathcal{U}(t, t_0).\label{eq:unitary_schroedinger}
		\end{align}

		Thus, to solve Equation~\eqref{eq:schroedinger} for $ \psi(t) $ given a particular $ \psi(t_0) $, one only needs to solve Equation~\eqref{eq:unitary_schroedinger} for $ \mathcal{U}(t, t_0) $.
		% Note that because $ \mathcal{U}(t, t_0) $ is unitary, the calculated value of $ \psi(t) $ using this method will not change in magnitude, conserving probability.
		Since $ \mathcal{U}(t, t_0) $ is unitary, it can be written as a matrix exponential of a anti-Hermitian (also termed skew-Hermitian) matrix.
		If the Hamiltonian is a of constant value $ H(t) = \mathcal{H} $, then this exponential is % \note{Should we use H, ie no argument, or H(t'), ie arbitrary argument, to represent constancy?} % Check if continuity requirement on unitary
		\begin{align}
			\mathcal{U}(t, t_0) &= \exp(-i (t - t_0) \mathcal{H}).\label{eq:exp_sol_of_constant}
		\end{align}
		% The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series~\cite{blanes_magnus_2009}, where
		For a time varying Hamiltonian, the general solution for $ \mathcal{U}(t, t_0) $ is much more complex, because it encapsulates the full solution to the time-dependent Schr\"{o}dinger equation.
		The well known Dyson series~\cite{kalev_integral-free_2020} gives an explicit expression for $ \mathcal{U}(t, t_0) $ in terms of multiple time integrals over nested time commutators of $ H(t') $.
		While the Dyson series has recently been used numerically~\cite{kalev_integral-free_2020}, it is challenging to work with because once truncated, it is in general no longer unitary.

		The Magnus series, in contrast, gives $ \mathcal{U}(t, t_0) $ in terms of an exponential of a series of anti-Hermitian operators, specifically
		\begin{align}
			\mathcal{U}(t, t_0) &= \exp\left(\Omega(t, t_0)\right) = \exp\left(\sum_{m = 1}^\infty \Omega_m(t, t_0)\right).
		\end{align}
		As such, the Magnus series explicitly preserves unitarity when truncated~\cite{magnus_exponential_1954}.
		The terms in the Magnus series are integrals over nested time commutators of the Hermitian matrix $ A(t') $, where, in the case of quantum mechanics, $ A(t') = -iH(t') $.
		For instance, the first three terms are~\cite{blanes_magnus_2009}
		\begin{align}
			\Omega_1(t, t_0) &= \int_0^t\mathrm{d}t_1A(t_1)\\
			\Omega_2(t, t_0) &= \frac12\int_{t_0}^t\mathrm{d}t_1\int_{t_0}^{t_1}\mathrm{d}t_2[A(t_1), A(t_2)]\\
			\Omega_3(t, t_0) &= \frac16\int_{t_0}^t\mathrm{d}t_1\int_{t_0}^{t_1}\mathrm{d}t_2\int_{t_0}^{t_2}\mathrm{d}t_3\left([A(t_1), [A(t_2), A(t_3)]] + [A(t_3), [A(t_2), A(t_1)]]\right),
		\end{align}
		where $ [X, Y] = XY - YX $ is the commutator.
		Note that, when truncated to first order, the Magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_{t_0}^t\mathrm{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation~\eqref{eq:exp_sol_of_constant}, with $ H(t) $ approximated by its average value over the interval $ [t_0, t] $.

		% Insert first few omegas here
		% Throw back to constant
		% Here each $ \Omega_m(t) $ are integrals over time commutators of $ H(t') $.
		% $ \Omega_1(t) $, for example, is $ \Omega_1(t) = H_\mathrm{av}t $, where $ H_\mathrm{av} $ is the average value of $ H $ over the interval being integrated over, which is the solution for when $ H $ is constant in time.
		% The terms $ \Omega_m(t) $ for $ m > 1 $ are corrections to this approximation. One can truncate the Magnus series before infinity to make a Mangus expansion, which can given an approximation for $ \mathcal{U}(t, t_0) $.
		% Importantly, any truncation of the Magnus expansion is unitary, meaning that probability will be conserved when used.

		Convergence of the Magnus series for $ \mathcal{U}(t, t_0) $ is not in general guaranteed, but it is under the condition that $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi \approx 1.08686870\dots $~\cite{blanes_magnus_2009}.
		% The loosest bound discovered for the convergence of a general Magnus series for $ \mathcal{U}(t, t_0) $ is $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < 1.08686870\dots $~\cite{blanes_magnus_2009}.
		% A Magnus series for $ \mathcal{U}(t, t_0) $ will be guaranteed to converge if $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi = 1.08686870\dots $~\cite{blanes_magnus_2009}.
		Furthermore, each subsequent term in the expansion increases in complexity rapidly.
		For these reasons, the Magnus expansion is generally used as a time-stepping method rather than a single step to solve the complete system.
		Designing a Magnus-based solver is a trade-off between the number of terms used in each expansion, and the number of time-steps used.
		Time stepping is based on the fact that time evolution operators can be split into a product via
		\begin{align}
			\mathcal{U}(t, t_0) &= \mathcal{U}(t, t_{n - 1})\mathcal{U}(t_{n - 1}, t_{n - 2})\cdots\mathcal{U}(t_2, t_1)\mathcal{U}(t_1, t_0).\label{eq:product_of_time_evolution}
		\end{align}
		Each of the time-evolution operators can be approximated by a Magnus expansion.

@@

			A simulation of a typical neural sensing experiment was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.

>>>>

\section{Paper Author Roles and Affiliations}
1. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Primary author of the released packages.\\
2. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Present address: Vienna Center for Quantum Science and Technology (VCQ), Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
	Author of first version of code.\\
3. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Present address: Department of Applied Mathematics and Theoretical Physics, Centre for Mathematical Sciences, University of Cambridge, Cambridge, UK.\\
	Optimization and extension to spin-one of first version of code.\\
4. School of Molecular Sciences, La Trobe University, PO box 199, Bendigo, Victoria 3552, Australia.\\
	Present address: Q-CTRL Pty. Ltd.\\
	Original conception of first version, and advice on current version of code.\\
5. Department of Electrical and Computer Systems Engineering, Monash University, Victoria 3800, Australia.\\
	Advice on numerical analysis.\\
6. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Original conception of released version of algorithm.

\section{Abstract}
	The \emph{Spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shr\"odinger equation.
	It makes use of \texttt{numba.cuda}, which is an \emph{LLVM} (Low Level Virtual Machine) compiler for \emph{Nvidia Cuda} compatible systems using GPU parallelization. 
	Along with other optimizations, this allows for speed improvements from 3 to 4 orders of magnitude while staying just as accurate, compared to industry standard packages. % Mention which ones?
	It is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
	The initial use-case for the \emph{Spinsim} will be to simulate quantum sensing-based ultracold atom experiments for the Monash University School of Physics \& Astronomy spinor Bose-Einstein condensate (spinor BEC) lab, but we anticipate it will be useful in simulating any range of spin-half or spin-one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
	These appear in the fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin-one systems of nitrogen vacancy centres (NVCs), ultracold atoms, and BECs.

@@

\section{Introduction}
\subsection{Motivation}
	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing~\cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
	The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
	The simplest spin system, spin-half (i.e.spin quantum number of $ \frac12 $, also referred to as a qubit), is quantized into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (i.e.spin quantum number of $ 1 $, also referred to as a quitrit), which is quantized into three quantum spin levels.

@@

	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours, or even multiple days.
	Given the recent boom in machine learning, many research computers are now equipped with modern graphics processing units (GPUs).
	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
	Examples include calculating color values for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
	While there do exists parallelized algorithms to solve general differential equations~\cite{lions_resolution_2001}, there are properties specific to the spin system that allow for much more fast and elegant parallelization in our use-case.
	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by up to 4 orders of magnitude.
	% Mention GPU in fewer words

@@

\section{Implementation and architecture}
	% \subsection{Mathematical methods}
	\subsection{Quantum mechanics background}
		The \emph{Spinsim} package solves the time-dependent Schr\"{o}dinger equation
		\begin{align}
			i\hbar\frac{\text{d}\psi(t)}{\text{d}t} &= H(t)\psi(t),\label{eq:schroedinger}
		\end{align}
		where the quantum state $ \psi(t) \in \mathbb{C}^N $ is assumed normalized, and the Hamiltonian $ H(t) \in \mathbb{C}^{N \times N} $ is Hermitian.
		Here $ N $ is the number of levels in the quantum system.
		Often we are considering systems with spin of half ($ N = 2 $ case) or one ($ N = 3 $).
		% Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
		% \supervisordisagreement{
		% 	Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
		% }{
		% Spin-half is the $ N = 2 $ case, and spin-one is the $ N = 3 $ case.
		% }
		We set $ \hbar = 1 $, so that the Hamiltonian has physical dimension of angular frequency.
		% Furthermore, we have chosen for the Hamiltonian $ H(t) $ to have the physical dimension of frequency, rather than the more typical dimension of energy. To elaborate, we represent energies $ E $ of the system as their equivalent frequencies $ f $ from the Planck relation

@@

		Rather than parametrizing the problem in terms of the matrix elements of $ H(t) $, we consider time varying real coefficients in a linear combination of a basis of fixed operators,
		\begin{align}
			H(t) &= \sum_{j = 1}^{N^2 - 1} \omega_j(t) \mathcal{A}_j.
		\end{align}
		Here we exclude the identity so that the Hamiltonian is traceless, which corresponds to choosing a physically meaningless energy zero point.
		It is well known~\cite[(p74)]{j_j_sakurai_jun_john_modern_2011} that a charged spin-half system with magnetic moment $ \overrightarrow{\mu} $, and gyromagnetic ratio $ \gamma $, in a magnetic field $ \overrightarrow{B}(t) $, has Hamiltonian
		\begin{align}
			H(t) &= -\overrightarrow{B}(t)\cdot \overrightarrow{\mu}\\
			% &= -\gamma \overrightarrow{B}(t)\cdot \overrightarrow{J}\\
			&= -\gamma \left(B_x(t) J_x + B_y(t) J_y + B_z(t) J_z\right)\\
			% &= \left(-\gamma B_x(t) J_x\right) + \left(-\gamma B_y(t) J_y\right) + \left(-\gamma B_z(t) J_z\right)\\
			&= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z.
		\end{align}
		Here $ J_x $, $ J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices~\cite[(p169)]{j_j_sakurai_jun_john_modern_2011} halved.
		% \supervisordisagreement{
		% 	Here $ J_x, J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices halved.
		% }{
		% 	Here $ J_x, J_y $ and $ J_z $ are spin operators
		% 	\begin{align}
		% 		J_x &= \frac12\begin{pmatrix}
		% 			0 & 1 \\
		% 			1 & 0
		% 		\end{pmatrix},
		% 		&J_y &= \frac12\begin{pmatrix}
		% 			0 & -i \\
		% 			i &  0
		% 		\end{pmatrix},
		% 		&\textrm{and }J_z &= \frac12\begin{pmatrix}
		% 			1 &  0 \\
		% 			0 & -1
		% 		\end{pmatrix},\label{eq:spin_half_operators}
		% 	\end{align}
		% 	equal to the Pauli matrices halved.
		% }
		Motivated by this, we define our basis for the spin-half model with $ \mathcal{A}_1 = J_x $, $ \mathcal{A}_2 = J_y $ and $ \mathcal{A}_3 = J_z $.
		Additionally, because of the equivalence of the magnetic field components $ B_j(t) $ and the $ \omega_j(t) $, we henceforth refer to the latter as field functions.

		In the spin-one case there is no universal standard basis of operators $ \mathcal{A}_j $.
		Choices include the Gell-Mann matrices~\cite{gell-mann_symmetries_1962}, and multiple dipole-quadrupole bases~\cite{hamley_spin-nematic_2012, di_dipolequadrupole_2010}.
		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
		We focus on a particular subfamily of of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x $, $ J_y $ and $ J_z $, (labelled $ L_x $, $ L_y $ and $ L_z $ in Reference~\cite{hamley_spin-nematic_2012}) and a single quadrupole operator $ Q = \text{diag}(1, -2, 1)/3 $,% \todo{Describe this subspace better}

@@

		% With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \text{diag}(1, -2, 1)/3 $,
		\begin{align}
			H(t) &= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q.
		\end{align}

		Note that $ Q $ is proportional to $ J_z^2 $ (up to a change in energy zero point), and $ Q_{zz} $~\cite{hamley_spin-nematic_2012} and $ Q_0 $~\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
		The $ J_x $, $ J_y $, $ J_z $ and $ Q $ are the only operators necessary to simulate many spin-one quantum systems in arbitrary bias fields, but with single-photon coupling.
		This includes quadratic Zeeman splitting described by the Breit-Rabi formula~\cite{mockler_atomic_1961}, important to experiments in our lab.
		The \emph{Spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $ using the full quadrupole basis, which extends the possible Hamiltonian to
		\begin{align}
			H(t) =& \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q\nonumber\\
			&+ \omega_{u1}(t) U_1 + \omega_{u2}(t) U_2 + \omega_{v1}(t) V_1 + \omega_{v2}(t) V_2.
		\end{align}
		Here the additional operators are those defined in~\cite{di_dipolequadrupole_2010}. Note that this is included for completeness, but has not been thoroughly tested, as our lab has no physical context for modelling the $ U_1, U_2, V_1 $ and $ V_2 $ operators.
		% In general ... Lie algebra ... mathfrak ... admits a basis ... .
		% \begin{align}
		% 	\frac{\text{d}}{\text{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z) \psi(t),
		% \end{align}

@@

		% \begin{align}
		% 	\frac{\text{d}}{\text{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z + f_q(t) Q) \psi(t).
		% \end{align}

@@

	\subsection{Unitary time evolution and the Magnus expansion}\label{sec:magnus}
		Since $H(t)$ is Hermitian, it follows from Equation~\eqref{eq:schroedinger} that $\|\psi(t)\|^2 = \|\psi(t_0)\|^2$ for all $t$.
		Therefore it is possible to write $ \psi(t) $ in terms of a unitary transformation $ \mathcal{U}(t, t_0) $ of the state $ \psi(t_0) $, for any time $ t_0 $, that is, $ \psi(t) = \mathcal{U}(t, t_0)\psi(t_0) $.
		It then follows from Equation~\eqref{eq:schroedinger} that $ \mathcal{U}(t, t_0) $ also follows a Schr\"{o}dinger equation,
		\begin{align}
			i\hbar\frac{\text{d}\mathcal{U}(t, t_0)}{\text{d}t} &= H(t)\mathcal{U}(t, t_0).\label{eq:unitary_schroedinger}
		\end{align}

		Thus, to solve Equation~\eqref{eq:schroedinger} for $ \psi(t) $ given a particular $ \psi(t_0) $, one only needs to solve Equation~\eqref{eq:unitary_schroedinger} for $ \mathcal{U}(t, t_0) $.
		% Note that because $ \mathcal{U}(t, t_0) $ is unitary, the calculated value of $ \psi(t) $ using this method will not change in magnitude, conserving probability.
		Since $ \mathcal{U}(t, t_0) $ is unitary, it can be written as a matrix exponential of a anti-Hermitian (also termed skew-Hermitian) matrix.
		If the Hamiltonian is a of constant value $ H(t) = \mathcal{H} $, then this exponential is % \note{Should we use H, i.e.no argument, or H(t'), i.e.arbitrary argument, to represent constancy?} % Check if continuity requirement on unitary
		\begin{align}
			\mathcal{U}(t, t_0) &= \exp(-i (t - t_0) \mathcal{H}).\label{eq:exp_sol_of_constant}
		\end{align}
		% The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series~\cite{blanes_magnus_2009}, where
		For a time varying Hamiltonian, the general solution for $ \mathcal{U}(t, t_0) $ is much more complex, because it encapsulates the full solution to the time-dependent Schr\"{o}dinger equation.
		The well known Dyson series~\cite{kalev_integral-free_2020} gives an explicit expression for $ \mathcal{U}(t, t_0) $ in terms of multiple time integrals over nested time commutators of $ H(t') $.
		While the Dyson series has recently been used numerically~\cite{kalev_integral-free_2020}, it is challenging to work with because once truncated, it is in general no longer unitary.

		The Magnus series, in contrast, gives $ \mathcal{U}(t, t_0) $ in terms of an exponential of a series of anti-Hermitian operators, specifically
		\begin{align}
			\mathcal{U}(t, t_0) &= \exp\left(\Omega(t, t_0)\right) = \exp\left(\sum_{m = 1}^\infty \Omega_m(t, t_0)\right).
		\end{align}
		As such, the Magnus series explicitly preserves unitarity when truncated~\cite{magnus_exponential_1954}.
		The terms in the Magnus series are integrals over nested time commutators of the Hermitian matrix $ A(t') $, where, in the case of quantum mechanics, $ A(t') = -iH(t') $.
		For instance, the first three terms are~\cite{blanes_magnus_2009}
		\begin{align}
			\Omega_1(t, t_0) &= \int_0^t\text{d}t_1A(t_1),\\
			\Omega_2(t, t_0) &= \frac12\int_{t_0}^t\text{d}t_1\int_{t_0}^{t_1}\text{d}t_2[A(t_1), A(t_2)],\\
			\Omega_3(t, t_0) &= \frac16\int_{t_0}^t\text{d}t_1\int_{t_0}^{t_1}\text{d}t_2\int_{t_0}^{t_2}\text{d}t_3\left([A(t_1), [A(t_2), A(t_3)]] + [A(t_3), [A(t_2), A(t_1)]]\right),
		\end{align}
		where $ [X, Y] = XY - YX $ is the commutator.
		Note that, when truncated to first order, the Magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_{t_0}^t\text{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation~\eqref{eq:exp_sol_of_constant}, with $ H(t) $ approximated by its average value over the interval $ [t_0, t] $.

		% Insert first few omegas here
		% Throw back to constant
		% Here each $ \Omega_m(t) $ are integrals over time commutators of $ H(t') $.
		% $ \Omega_1(t) $, for example, is $ \Omega_1(t) = H_\text{av}t $, where $ H_\text{av} $ is the average value of $ H $ over the interval being integrated over, which is the solution for when $ H $ is constant in time.
		% The terms $ \Omega_m(t) $ for $ m > 1 $ are corrections to this approximation. One can truncate the Magnus series before infinity to make a Mangus expansion, which can given an approximation for $ \mathcal{U}(t, t_0) $.
		% Importantly, any truncation of the Magnus expansion is unitary, meaning that probability will be conserved when used.

		Convergence of the Magnus series for $ \mathcal{U}(t, t_0) $ is not in general guaranteed, but it is under the condition that $ \int_{t_0}^t\text{d}t_1\|H(t_1)\|_2 < \xi \approx 1.08686870\dots $~\cite{blanes_magnus_2009}.
		% The loosest bound discovered for the convergence of a general Magnus series for $ \mathcal{U}(t, t_0) $ is $ \int_{t_0}^t\text{d}t_1\|H(t_1)\| < 1.08686870\dots $~\cite{blanes_magnus_2009}.
		% A Magnus series for $ \mathcal{U}(t, t_0) $ will be guaranteed to converge if $ \int_{t_0}^t\text{d}t_1\|H(t_1)\| < \xi = 1.08686870\dots $~\cite{blanes_magnus_2009}.
		Furthermore, each subsequent term in the expansion increases in complexity rapidly.
		For these reasons, the Magnus expansion is generally used as a time-stepping method rather than a single step to solve the complete system.
		Designing a Magnus-based solver is a trade-off between the number of terms used in each expansion, and the number of time-steps used.
		Time stepping is based on the fact that time evolution operators can be split into a product via
		\begin{align}
			\mathcal{U}(t, t_0) &= \mathcal{U}(t, t_{n - 1})\mathcal{U}(t_{n - 1}, t_{n - 2})\cdots\mathcal{U}(t_2, t_1)\mathcal{U}(t_1, t_0).\label{eq:product_of_time_evolution}
		\end{align}
		Each of the time-evolution operators can be approximated by a Magnus expansion.

@@

			A simulation of a typical sensing experiment for our lab was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
			In the simulation, transitions are continuously driven in the spin system for a duration of $ 100 \,\text{ms} $, and an additional small signal is injected for $ 1\,\text{ms} $.
